---
title: "Blog Code Style Guide"
author: "Aiden Ross"
date: "03/06/26"
format: html
---

# purpose

This page is intended to be a living document. As preferences change and I become more informed, I may update certain aspects. This document defines the structure I expect and helps enforce consistency in my code. 

# variable and function names

## single char names

R is often used for quick computations. If a value is not needed beyond a single step, single-character variable names are acceptable.

```{r}
# simplistic for short code 

x <- 10
x 
```

## snake case

Snake case is usually clear and easy to read for short blocks of code.

```{r}

# be specific given some context
some_variable <- 1203

some_variable

```

## pascal case

Pascal case is my preferred style for functions in rcode. This convention also helps distinguish user-defined functions from library functions.

```{r}

# a function name should state its purpose

SquaredValue <- function(x) {
    return (x * x)
}

SquaredValue(5)

```
