---
title: "Blog Code Style Guide"
author: "Aiden Ross"
date: "03/06/26"
format: html
---

# purpose 

This page is intended to be a living document. As preferences changes and I become more informed I may update certain things. Roughly, this is supposed to be a place to show the structure to expect and more importantly to keep me consistent.

# variable and function names

## single char names

Often, rcode is used for quick computations; As long as the value is not important beyond a single chunk I will allow the use of single character variable names.

```{r}
# simplistic for short code 

x <- 10
x 
```

## snake case 
Snake case is usually clear and easy to read for short blocks of code.

```{r}

# be specific given some context
some_variable <- 1203

some_variable

```

## pascal case

Pascal case is preferred for functions in rcode. 

```{r}

# a function name should state its purpose
# also do note that this primarily
# is to be able to tell functions I write from library functions
SquaredValue <- function(x) {
    return (x * x)
}

SquaredValue(5)

```