---
title: "How to Import and Analyze Phyphox CSV Data in RStudio"
author: "Aiden Ross"
date: "2026-02-18"
date-modified: last-modified
categories: [data, statistics, phyphox]
format: html
---

The phyphox app is a really cool way to collect your own data. You can read more about it here: [phyphox](#0 "source website")

```{r}
library(tidyverse)
```

# Import Phyphox Data

It is super easy to get a dataset to work with from phyphox.

1.  collect your data.\n
2.  In the data collection screen click the three dots in the upper right corner and click export data.\n
3.  select **CSV (Comma, decimal point)** or anything you want but that one is easy to use.\n
4.  Download the csv file and move it to you rcode project working directory.

Here is some data I collected this morning on my way to class.

```{r}
# A short collection of gyro data
gyro <- read_csv("./data/gyro.csv", show_col_types = FALSE) |> 
  rename(time=`Time (s)`, xrot=`Gyroscope x (rad/s)`, yrot=`Gyroscope y (rad/s)`, zrot=`Gyroscope z (rad/s)`, absolute=`Absolute (rad/s)`)

# A collection of walking data
walk <- read_csv("./data/aidenr-walk.csv", show_col_types = FALSE)


gyro |> head()
walk |> head()
```

# Usage

After importing the data we can use it like any other dataset in R. Here is a brief look.

The gyro data was collected before I left the car. This shows how it measures rotation. The shape of the graph comes from my rotation of the phone. As you see it accelerates but returns to a baseline (notice the small accelerations of my imperfect human hand and possible measurement errors at the baseline).

```{r}

ggplot(data = gyro, aes(x = time,y = xrot)) +
  geom_point(color="#ff0f00", size = 1) +
  labs(title = "Gyro x vs. time", x = "Time (s)", y = "x (rad/s)")

ggplot(data = gyro, aes(x = time,y = yrot)) +
  geom_point(color="#00a10a", size = 1) +
   labs(title = "Gyro y vs. time", x = "Time (s)", y = "y (rad/s)")

ggplot(data = gyro, aes(x = time, y = zrot)) +
    geom_point(color="#00a1aa", size = 1) +
   labs(title = "Gyro z vs. time", x = "Time (s)", y = "z (rad/s)")
```

# Analyzing GPS Walking Data from Phyphox

## GPS Safety

GPS data sets have precise **longitude** and **latitude** values. Share raw data cautiously to avoid leaking private data. (*note: this is also useful for geometry. The earth can be seen as a sphere and this data can be converted spherical coordinates*)

## Data Source

In this set I am in a public place and recording a **~6 minute** walk that is not anywhere near my home. 

```{r}
# show a data sample
glimpse(walk)
```

## Linear Equations

Here is the fun part: we can use calculus and linear geometry to analyse this data. 

```{r}

ggplot(data=walk, aes(x=`Time (s)`, y=`Distance (km)`, color=`Direction (°)`)) +
  geom_point() +
  theme_gray()

```

Above you can see that distance is approximately a line. This means we can use the equation $$y=mx+b$$ to help us analyse it. After observing the graph we can tell my walk was at roughly a constant speed and direction.  

```{r}
ggplot(data=walk, aes(x=`Time (s)`, y=`Distance (km)`)) +
  geom_smooth(method="lm") +
  theme_gray()
```
Now, how do we get the slope of this line? Well, rcode can do this for us. You can also do it the old fashion way if you want.

```{r}
summary(lm(`Distance (km)` ~ `Time (s)`, data=walk))
```
```{r}
ggplot(data=walk, aes(x=`Time (s)`, y=`Altitude (m)`, color=`Vertical Accuracy (m)`)) +
  geom_point() +
  geom_smooth(method="lm")
```
